### 2019-01-01 papers/journal/intro.tex
small fixes

In this section, we will abstract from the biological description of a VTS and represent the whole network as an annotated transport graph. 
%
The constraints imposed by cell biology is incorporated in the  annotations of the graph.

@@

The rest of the paper is organized as follows. 
%
In Sect.~\ref{sec:prelim}, we present the notations we use in this paper. 
%
In Sect.~\ref{sec:model}, we present graph model of VTSs.
%
%encoding of several constraints on VTSs. 
%
In Sect.~\ref{sec:property}, we present the properties of interest.
%
In Sect.~\ref{sec:problem}, we present formal problem statement of the verification properties.
%
In Sect.~\ref{sec:encoding}, we present the encoding of BMC, SMT, QBF and Synthesis into SAT, SMT and QBF satisfiability. 
%
In Sect.~\ref{sec:experiments}, we present our implementation and experimental results. 
%
In Sect.~\ref{sec:related}, we discuss related work and conclude in Sect.~\ref{sec:conclusion}.

>>>>

In this section, we will abstract from the biological description of the VTS and represent the whole network as an annotated transport graph. 
%
The constraints imposed by cell biology is incorporated in the  annotations of the graph.

@@

The rest of the paper is organized as follows. 
%
In Sect.~\ref{sec:prelim}, we present the notations we use in this paper. 
%
In Sect.~\ref{sec:model}, we present graph model of VTSs and  properties of interest in Sect.~\ref{sec:property}.
%
%encoding of several constraints on VTSs. 
%
%In , we present the
%
In Sect.~\ref{sec:problem}, we present the complete formal problem statement of the verification properties.
%
In Sect.~\ref{sec:encoding}, we present the encoding of BMC, SMT, QBF and Synthesis into SAT, SMT and QBF satisfiability. 
%
In Sect.~\ref{sec:experiments}, we present our implementation and experimental results. 
%
In Sect.~\ref{sec:related}, we discuss related work and conclude in Sect.~\ref{sec:conclusion}.
